---
title: "Lab 02 - Plastic waste"
author: "Insert your name here"
date: "Insert date here"
output: html_document
---

## Load packages and data

```{r setup, message=FALSE}
library (tidyverse)
```

```{r load-data, message=FALSE}
install.packages("here")
plastic_waste <- read_csv(here::here("data", "plastic-waste.csv"))
```

## Exercises
```{r}
ggplot(data = plastic_waste) +
  aes(x = plastic_waste_per_cap) +
  geom_histogram(binwidth = 0.2)
```
```{r}
plastic_waste |>
  filter(plastic_waste_per_cap > 3.5)
```
### Exercise 1
```{r plastic-waste-continent}
ggplot(plastic_waste) +
  aes(x = continent, y = waste, fill = "pink") +
  geom_density(aes(y = after_stat(count), color = continent, alpha = .1)) 
```
1. alpha went with geom becasue it was referring to the densities (which are the aesthetic used)

2. color and fill went into the aesthetics because it was referring to the shapes 


### Exercise 2

```{r plastic-waste-density}
ggplot(plastic_waste) +
  aes(x = continent,
      y = plastic_waste_per_cap,
      fill = continent) +
  geom_boxplot(color = "black",
               alpha = .5) +
  geom_density(alpha = .1)
```

### Exercise 3
```{R}
ggplot(plastic_waste) +
  aes(x = continent,
      y = plastic_waste_per_cap,
      color = continent) +
  geom_point(alpha = .5)
```
```{R}
ggplot(plastic_waste) +
  aes(x = coastal_pop,
      y = plastic_waste_per_cap,
      color = continent) +
  geom_point(alpha = .5) +
  geom_line()
```
```{R}
ggplot(plastic_waste) +
  aes(x = total_pop,
      y = plastic_waste_per_cap,
      color = continent) +
  geom_point(alpha = .5) +
  geom_line()
```
### Exercise 4

Remove this text, and add your answer for Exercise 4 here.

```{r plastic-waste-violin}
# insert code here
```

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.

```{r plastic-waste-mismanaged}
# insert code here
```

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.

```{r plastic-waste-mismanaged-continent}
# insert code here
```

### Exercise 7

Remove this text, and add your answer for Exercise 7 here.

```{r plastic-waste-population-total}
# insert code here
```

```{r plastic-waste-population-coastal}
# insert code here
```

### Exercise 8

Remove this text, and add your answer for Exercise 8 here.

```{r recreate-viz}
# insert code here
```

## Pro-Tips

### Excercise 3

Try this :D

```
ggplot(data = plastic_waste, 
       mapping = aes(x = continent, 
                     y = plastic_waste_per_cap)) +
  geom_violin()+
  geom_boxplot(width=.3, fill="green") +
  stat_summary(fun.y=median, geom="point") 
```

### Exercise 5 

Helpful reference:http://www.sthda.com/english/wiki/ggplot2-themes-and-background-colors-the-3-elements


