---
title: "Lab-402152022"
author: "Angelina Venetto"
date: "2/15/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(tidyverse)
library(dplyr)
```

```{r}
dictionary <- readr::read_csv(here::here("progdata-class", "data", "green_dictionary.csv"))
green_data <- readr::read_csv(here::here("progdata-class", "data", "green_data.csv"))
```
#QUESTION 1.

#check histograms 
```{r}
green_data |>
  pull(green1) |>
  hist()
```
```{r}
green_data |>
  pull(open10) |>
  hist()
```
#find unique values in Open 10
```{r}
green_data |>
  pull(open10) |>
  unique()
```
#Recode all columns exept ID to get rid of -99
```{r}
green_data <- green_data |>
  mutate (
    across(
      -id,
      \(x) recode(x, "1" = 1, "2" = 2, "3" = 3,"4" = 4, "5" = 5, "-99" = NA_real_)
    )
  )
```
    )
  )
#QUESTION 2.
#pull items that need to be reverse scored, use pull to get just the vector. 
```{r}
reversed <- dictionary |>
  filter(Keying == -1) |>
  pull(Item)
```
#reverse score 
##comp 6 = taking highest number (5), adding to lowest number(1), subtracting all scores from that number (6)
```{r}
green_data <- green_data |>
  mutate(
    green2 = recode(green2, "1" = 5, "2" = 4, "3" = 3, "4" = 2, "5" = 1))
    comp = max(comp6, na.rm = TRUE) - min(comp6, na.rm = TRUE) comp6
    
  )
```
#This way is cleaner because you can assign to all reverse columns at once, since i created the "reverse" ovject out of the reverse score coulumns previously
```{r}
green_data <- green_data |>
  mutate(
    across(
     all_of(reversed),
     \(x) recode(x, "1" = 5, "2" = 4, "3" = 3, "4" = 2, "5" = 1)
    )
    
  )
```
#create reverse item function 
```{r}
reverse_item <- \(x)
{ recode(x, "1" = 5, "2" = 4, "3" = 3, "4" = 2, "5" = 1)}

reverse_item(1:5)
```
#Compute total scores
```{r}
green_data <- green_data |>
  rowwise() |>
  mutate(
    green_total = mean(c_across(green1:green5), na.rm = TRUE),
    comp_total = mean(c_across(comp1:comp10), na.rm = TRUE),
    intel_total = mean(c_across(intel1:intel10), na.rm = TRUE),
    open_total = mean(c_across(open1:open10), na.rm = TRUE),
    .after = id
) |>
  ungroup()
  green_data
```
#Question 3
#Rescale variable to go from 0-100
```{r}
green_data <- green_data |>
  mutate(
    across(
      green_total:open_total,
      \(x) 100 * (x - 1) / (5 - 1),
      .names = "{.col}_pomp"
      ),
    .after = open_total
  )
green_data
```
#Question 4
#make a plot to illustrate POMP
```{r}
